---
title: "Staff Absences"
author: "Fiona Spooner"
date: "03/04/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

Libraries
```{r}
library(readxl)
library(data.table)
library(dplyr)
library(ggplot2)
library(janitor)
library(tidyr)
```

```{r}
end_date <- as.Date("2020-04-16")

```
Loading Data
```{r}
Daily_Absences_All_Staff <-
  read_excel(
    "Data/Data_from_Claire/Staff_Absences_RDE_20200403.xlsx",
    "Daily_Absences_All_Staff",
    col_names = TRUE
  ) %>% 
  mutate(Staff_Absences_Perc = Staff_Absences_Perc/100, 
         Staff_Absences_Covid_Perc = Staff_Absences_Covid_Perc/100)

Daily_Absences_All_Staff$Staff_Absences_NoCovid_Perc = Daily_Absences_All_Staff$Staff_Absences_Perc -
  Daily_Absences_All_Staff$Staff_Absences_Covid_Perc

```

Scenario Data
```{r}

load("Data/Data_from_Claire/ScenariosRDE.RData")

scenRDE <- ScenariosRDE %>% 
  filter(Date <= end_date) %>% 
  mutate(Doubling_lag = c(NA, Doubling[-length(Doubling)]), Rt50_lag = c(NA, ImpMedian[-length(ImpMedian)]), Rt75_lag = c(NA, Imp75[-length(Imp75)]), Doubling_pcnt = (Doubling/Doubling_lag), Rt50_pcnt = (ImpMedian/Rt50_lag), Rt75_pcnt = (Imp75/Rt75_lag)) #%>%   select(Date, Doubling_pcnt, Rt50_pcnt, Rt75_pcnt)


scenRDE[1,] <- scenRDE[2,]


scenRDE$RtDoubling <- tail(Daily_Absences_All_Staff$Staff_Absences_Covid_Perc,1) * cumprod(scenRDE$Doubling_pcnt)

scenRDE$Rt50 <- tail(Daily_Absences_All_Staff$Staff_Absences_Covid_Perc,1) * cumprod(scenRDE$Rt50_pcnt)

scenRDE$Rt75 <- tail(Daily_Absences_All_Staff$Staff_Absences_Covid_Perc,1) * cumprod(scenRDE$Rt75_pcnt)
```

```{r}
dates <-
  seq(max(as.Date(Daily_Absences_All_Staff$Date)), end_date, by = "day")

cov_df <-
  data.frame(
    date = c(as.Date(Daily_Absences_All_Staff$Date), dates[-1]),
    Doubling = c(
      Daily_Absences_All_Staff$Staff_Absences_Covid_Perc,
      scenRDE$RtDoubling
    ),
    Rt50 =  c(
      Daily_Absences_All_Staff$Staff_Absences_Covid_Perc,
      scenRDE$Rt50
    ),
    Rt75 =  c(
      Daily_Absences_All_Staff$Staff_Absences_Covid_Perc,
      scenRDE$Rt75
    )
  )
```

```{r}
cov_long <-
  cov_df %>% pivot_longer(., c("Doubling", "Rt50", "Rt75"))

ggplot(cov_long %>% filter(date > as.Date("2020-03-19")), aes(x = date, y = value, group = name))+
  geom_point()+
  geom_smooth()+
  facet_wrap(~name)+
  ggtitle("Rt for RDE")

```

No Cov Absences
```{r}
daily_abs_dates <-
  seq(min(as.Date(Daily_Absences_All_Staff$Date)), max(cov_long$date), by = "day")

daily_abs <-
  c(
    Daily_Absences_All_Staff$Staff_Absences_NoCovid_Perc,
    rep(
      tail(Daily_Absences_All_Staff$Staff_Absences_NoCovid_Perc, 1),
      length(daily_abs_dates) - length(Daily_Absences_All_Staff$Staff_Absences_NoCovid_Perc)
    )
  )

no_cov_abs <-
  data.frame(date = daily_abs_dates, no_cov_abs = daily_abs)

no_cov_abs <- no_cov_abs %>% 
  filter(date >= min(cov_df$date))
```

Staff Group Data
```{r}

Number_Staff_By_Group <- read_excel("Data/Data_from_Claire/Staff_Absences_RDE_20200403.xlsx", "Number_Staff_By_Group", col_names = TRUE) %>% 
  select(Group, FTE, Number_Staff) %>% 
  filter(!Group %in% c("Students", "Total"))

Number_Staff_By_Group$FTE <- as.numeric(Number_Staff_By_Group$FTE)

Number_Staff_By_Group$Number_Staff <- as.numeric(Number_Staff_By_Group$Number_Staff)

```

Group Weights

```{r}
Absences_By_Group <- read_excel("Data/Data_from_Claire/Staff_Absences_RDE_20200403.xlsx", "Absences_By_Group",col_names = TRUE) %>% 
  filter(!Group %in% c("Total", "Students")) %>% 
  left_join(., Number_Staff_By_Group, by = "Group") %>% 
  mutate(Staff_Absences_Perc = as.numeric(Staff_Absences_Perc)/100,
         Staff_Absences_Covid_Perc = as.numeric(Staff_Absences_Covid_Perc)/100)


Absences_By_Group$Num_Absent <- Absences_By_Group$Staff_Absences_Covid_Perc *Absences_By_Group$Number_Staff

Absences_By_Group$Weights_Covid_Absences_By_Group <- Absences_By_Group$Num_Absent/sum(Absences_By_Group$Num_Absent)


staff_weights <- left_join(Number_Staff_By_Group, Absences_By_Group) %>% 
  select(Group, Number_Staff,Staff_Absences_Covid_Perc,Weights_Covid_Absences_By_Group) %>% 
  filter(!Group %in% c("Students", "Total"))
```

```{r}

combs <-
  expand.grid(group = unique(staff_weights$Group),
              model = unique(cov_long$name))

group_df <- data.frame()
for (i in 1:nrow(combs)) {
  group = combs$group[i]
  model = combs$model[i]
  
  staff_group <- staff_weights %>%
    filter(Group == group)
  
  cov_rates <- cov_long %>%
    filter(name == model)
  
  cov_staff_out <-
    sum(staff_weights$Number_Staff) * staff_group$Weights_Covid_Absences_By_Group * cov_rates$value
  no_cov_staff_out <-
    sum(staff_weights$Number_Staff) * staff_group$Weights_Covid_Absences_By_Group * no_cov_abs$no_cov_abs
  total_staff_out <- cov_staff_out + no_cov_staff_out
  
  num_staff <-  staff_group$Number_Staff
  group_out <- data.frame(
    date = cov_df$date,
    group = group,
    model = model,
    cov_staff_out = cov_staff_out,
    no_cov_staff_out = no_cov_staff_out,
    total_staff_out = total_staff_out,
    num_staff = num_staff,
    cov_prop_staff_out = (cov_staff_out / num_staff) *
      100,
    no_cov_prop_staff_out = (no_cov_staff_out / num_staff) *
      100,
    total_prop_staff_out = (total_staff_out / num_staff) *
      100
  )
  
  group_df <- rbind(group_out, group_df)
}


```

```{r, warnings =FALSE}

#2 week lag - people returning after 2 weeks

group_df_lag <- group_df %>%
  group_by(group, model) %>%
  mutate(
    nrows = n(),
    end_lag = nrows[1] - 14 ,
    cov_staff_return = ifelse(nrows > 14, c(rep(0, 14), cov_staff_out[1:end_lag]), 0),
    cov_lag_staff_out = cov_staff_out - cov_staff_return,
    cov_lag_prop = (cov_lag_staff_out / num_staff) * 100
  ) %>%
  ungroup() %>%
  mutate(
    total_staff_out = cov_lag_staff_out + no_cov_staff_out,
    total_prop_staff_out = (total_staff_out / num_staff) * 100
  ) %>%
  mutate(data_type = ifelse(date <= max(as.Date(
    Daily_Absences_All_Staff$Date
  )), "Real", "Estimate")) %>%
  select(
    date,
    group,
    model,
    data_type,
    cov_staff_out,
    cov_lag_staff_out,
    cov_staff_return,
    no_cov_staff_out,
    total_staff_out,
    cov_prop_staff_out,
    cov_lag_prop,
    no_cov_prop_staff_out,
    total_prop_staff_out
  )


```

Staff groups

```{r}
num_pl_df <- data.frame(group_df_lag %>% 
  select(date, group, model,total_staff_out, cov_lag_staff_out, data_type) %>% 
  pivot_longer(., cols = c("total_staff_out", "cov_lag_staff_out")))

```

All Staff

```{r}
all_staff<- data.frame(num_pl_df %>% 
              group_by(date, model, name) %>% 
              summarise(value = sum(value)) %>%               select(date, model,  name, value) %>% 
              ungroup())
```

Group Plot

```{r}

num_plot <-
  ggplot(
    num_pl_df %>% filter(date > as.Date("2020-03-19")),
    aes(
      x = date,
      y = value,
      col = model,
      group = interaction(model, group, name)
    )
  ) +
  #geom_point(aes(shape = data_type), size = 1)+
  geom_point() +
  geom_smooth(aes(linetype = name)) +
  geom_vline(xintercept = as.Date("2020-04-01"), linetype = "dotted") +
  facet_wrap( ~ group) +
  ylab("Number Staff Absent") +
  xlab("Date") +
  scale_linetype_discrete(name = "Absence Type", labels = c("Covid", "Total Absent")) +
  #scale_shape_discrete(name = "Data Type", labels = c("Estimate", "Real"))+
  scale_color_discrete(name = "Model",
                       labels = c("Doubling", "Rt50", "Rt75")) +
  #guides(col = guide_legend(reverse=TRUE))
  theme_bw() +
  ggtitle("Staff Numbers Absent - NDDH")


num_plot

#ggsave("Outputs/RDE_Absences_Numbers_TNC_scen_Staff_Groups.png", width = 30, height = 20, units = "cm")

 num_pl_df %>% filter(model == "Rt50" & date == as.Date("2020-04-01")) %>% summarise(sum = sum(value))

```


All Staff Plot
```{r}

all_staff_plot <- ggplot(all_staff %>% filter(date > as.Date("2020-03-19")),aes(x = date, y = value, col = model, group = interaction(model,name)))+
 #geom_point(aes(shape = data_type), size = 1)+
  geom_point()+
  geom_smooth(aes(linetype = name))+
  geom_vline(xintercept = as.Date("2020-04-01"),linetype = "dotted")+
  ylab("Number Staff Absent")+
  xlab("Date")+
  scale_linetype_discrete(name = "Absence Type", labels = c("Covid", "Total Absent"))+
  scale_color_discrete(name = "Model", labels = c("Doubling", "Rt50","Rt75"))+
  #guides(col = guide_legend(reverse=TRUE))
  theme_bw()+
  ggtitle("Staff Numbers Absent - NDDH")


all_staff_plot

#ggsave("Outputs/RDE_Absences_Numbers_TNC_scen_All_Staff.png", width = 30, height = 20, units = "cm")

```

Proportion Plots
```{r}

prop_pl_df <- group_df_lag %>% 
  select(date, group, model,total_prop_staff_out, cov_lag_prop, no_cov_prop_staff_out, data_type) %>% 
  pivot_longer(., cols = c("total_prop_staff_out", "cov_lag_prop"))

prop_plot <- ggplot(prop_pl_df %>% filter(date > as.Date("2020-03-19")),aes(x = date, y = value, col = model, group = interaction(model, group,name)))+
  geom_point()+
  geom_smooth(aes(linetype = name))+
  geom_vline(xintercept = as.Date("2020-04-01"),linetype = "dotted")+
  facet_wrap(~group)+
  ylab("Proportion Staff Absent %")+
  xlab("Date")+
  scale_linetype_discrete(name = "Absence Type", labels = c("Covid", "Total Absent"))+
  scale_color_discrete(name = "Model", labels = c("Doubling","Rt50","Rt75"))+
  theme_bw()+
  ggtitle("Percentage Staff Absent - NDDH")


prop_plot

#ggsave("Outputs/RDE_Absences_Proportions_TNC_scen_Staff_Groups.png", width = 30, height = 20, units = "cm")

```


All Staff Prop
```{r}
total_staff <- sum(Number_Staff_By_Group$Number_Staff[1:8])

all_staff$prop_value <- all_staff$value /total_staff


all_props <- ggplot(all_staff %>% filter(date > as.Date("2020-03-19")),aes(x = date, y = prop_value, col = model, group = interaction(model, name)))+
  geom_point()+
  geom_smooth(aes(linetype = name))+
  geom_vline(xintercept = as.Date("2020-04-01"),linetype = "dotted")+
  ylab("Proportion Staff Absent %")+
  xlab("Date")+
  scale_linetype_discrete(name = "Absence Type", labels = c("Covid", "Total Absent"))+
  scale_color_discrete(name = "Model", labels = c("Doubling","Rt50","Rt75"))+
  theme_bw()+
  ggtitle("Percentage Staff Absent - NDDH")

#ggsave("Outputs/RDE_Absences_Proportions_TNC_scen_All_Staff.png", width = 30, height = 20, units = "cm")
