---
date: "`r Sys.Date()`"
output: pdf_document
params:
  hospital: "RDE"
  in_file: "Staff_Absences_RDE_20200422.xlsx"
  plot_start_date: !r as.Date("2020-03-29")
  end_date: !r as.Date("2020-05-13")
  in_dir: "C:/Users/Fiona/University of Exeter/COVID19 Modelling - Documents/Staff_Absences/Data_from_Claire/"
  out_dir: !r paste0("C:/Users/Fiona/University of Exeter/COVID19 Modelling - Documents/Staff_Absences/Reports_and_Results/Outputs_No_Return_",format(Sys.Date(), "%Y%m%d"), "/") 
  fig_width: 11.75
  fig_height: 7
  image_ppi: 1000
title: "Staff Absences - No Returners"
subtitle: "`r params$hospital`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = params$fig_width, fig.height = params$fig_height)
```

```{r}
library(readxl)
library(dplyr)
library(ggplot2)
library(here)
library(janitor)
library(knitr)
library(patchwork)
library(tidyr)

```


```{r}
Daily_Absences_All_Staff <-
  read_xlsx(paste0(
    params$in_dir,
    params$in_file
  ),
    sheet = "Daily_Absences_All_Staff",
    col_names = TRUE
  ) %>% 
  select(Date, Staff_Absences_Perc, Staff_Absences_Covid_Perc) %>% 
  mutate_if(is.character, as.numeric) %>% 
  mutate(Staff_Absences_Perc = Staff_Absences_Perc/100, 
         Staff_Absences_Covid_Perc = Staff_Absences_Covid_Perc/100,
         Staff_Absences_NoCovid_Perc = Staff_Absences_Perc - Staff_Absences_Covid_Perc, 
         Date = as.Date(Date)) %>% 
  select(Date, Staff_Absences_Perc, Staff_Absences_Covid_Perc, Staff_Absences_NoCovid_Perc)

```

```{r}

first_date <- as.Date(max(Daily_Absences_All_Staff$Date))

```

```{r}

load(paste0(params$in_dir, "Devon_projection2020-04-15.RData"))
scen_in <- Devon_projection

if (!first_date %in% scen_in$Date){
  
  days_missing <- min(scen_in$Date) - first_date
  dates <- seq(first_date, min(scen_in$Date)-1, by = "day")
  rep_data <- scen_in %>% slice(rep(1, each = days_missing))
  rep_data$Date <- dates
  scen_in <- rbind(rep_data, scen_in)
  
  }

if (!dir.exists(params$out_dir)){
  dir.create(params$out_dir, recursive = T)
}

# start_scen <- data.frame(Date = as.Date("2020-04-15"), Devon = 442, Italy = 442, Spain =442, UK = 442, London = 442)
#   
# scen_in <- rbind(start_scen, scen_in)
scenarios <- colnames(scen_in)[-1]

```

#### Modelled Forecasts\

Based on staff absence data over the period 19th March to 21st April, after which it is assumed that the number of staff absent with COVID-19 or in self-isolation will increase in proportion to the scenarios detailed above.

Here we forecast the staff absences for `r params$hospital` under five scenarios:

* `r scenarios[1]` - Using the PHE reported cases in Devon, we calculate the percentage day-to-day increase in cases. We then fit a model to this data to find the underlying trend (similar to using a moving average to smooth out day-to-day fluctuations) and to allow us to predict into future. This is referred to below as the ‘Devon curve’. 
* `r scenarios[2]` - We assume that Devon is behind `r scenarios[2]` in its curve and so we shift the Devon curve to align with the slope of the curve for `r scenarios[2]`. The exact number of days for the shift is chosen automatically and is around 2 weeks. 
* `r scenarios[3]`- We assume that Devon is behind `r scenarios[3]` in its curve and so we shift the Devon curve to align with the slope of the curve for `r scenarios[3]`. The exact number of days for the shift is chosen automatically and is around 2 weeks. 
* `r scenarios[4]` - As for Spain and Italy we shift the Devon curve to align with the slope of the curve for `r scenarios[4]`.
* `r scenarios[5]` - As for Spain and Italy we shift the Devon curve to align with the slope of the curve for `r scenarios[5]`.

We use these curves to predict future day-to-day increases in the staff absences in `r params$hospital`.



Assumptions:

`r if(params$hospital == "NDDH"){paste0("Daily ", params$hospital, " COVID-19 related absences have declined from ", Daily_Absences_All_Staff$Staff_Absences_Covid_Perc[Daily_Absences_All_Staff$Date == as.Date("2020-04-07")]*100, "% on ", as.Date("2020-04-07"), " to ",Daily_Absences_All_Staff$Staff_Absences_Covid_Perc[Daily_Absences_All_Staff$Date == as.Date("2020-04-21")]*100, "% on ", as.Date("2020-04-21"),".")}`

`r if(params$hospital == "RDE"){paste0("Daily ", params$hospital, " COVID-19 related absences have declined from ", Daily_Absences_All_Staff$Staff_Absences_Covid_Perc[Daily_Absences_All_Staff$Date == as.Date("2020-04-07")]*100, "% on ", as.Date("2020-04-07"), " to ",Daily_Absences_All_Staff$Staff_Absences_Covid_Perc[Daily_Absences_All_Staff$Date == as.Date("2020-04-21")]*100, "% on ", as.Date("2020-04-21"),".")}`


Absence by staff group based on data from April 21st

```{r, eval = FALSE}
# ######delete when real data is available - just continuing last available point of real data forwards until april 16th - will replace when data is available
# 
# dummy_df <- data.frame(Date = seq(as.Date("2020-04-08"), as.Date("2020-04-15"), by = "day"), Staff_Absences_Perc = tail(Daily_Absences_All_Staff$Staff_Absences_Perc,1),Staff_Absences_Covid_Perc = tail(Daily_Absences_All_Staff$Staff_Absences_Covid_Perc,1),  Staff_Absences_NoCovid_Perc = tail(Daily_Absences_All_Staff$Staff_Absences_NoCovid_Perc,1))
# 
# 
# Daily_Absences_All_Staff <-  rbind(Daily_Absences_All_Staff, dummy_df)

```



```{r Scenario Scaling Function}
scenario_scaler <- function(scenario_name, name_out,real_data, start_date_model, end_date_model){
  
  scen <- scen_in[,c("Date", scenario_name)]
  scen <- scen[scen$Date >= start_date_model & scen$Date <= end_date_model,]
  scen$scen_lag <- c(NA, head(scen[,scenario_name],-1))
  scen$scen_lag[1] <- scen$scen_lag[2]
  scen$scen_pcnt <- scen[,scenario_name]/scen$scen_lag
  scen$scen_rt <- cumprod(scen$scen_pcnt)
  scen$scen_model_pred <- tail(real_data, 1) * scen$scen_rt
  
  df_out <- data.frame(dates_out = seq(start_date_model - (length(real_data)-1), end_date_model, by = "day"),
                       pred_out = c(head(real_data,-1), scen$scen_model_pred),
                       model_name = name_out)
  return(df_out)  
  
}

```




```{r Scaling scenarios}
devon <- scenario_scaler(scenario_name = "Devon",
                name_out = "Devon",
                real_data = Daily_Absences_All_Staff$Staff_Absences_Covid_Perc,
                start_date_model = first_date, 
                end_date_model = params$end_date)

italy <- scenario_scaler(scenario_name = "Italy",
                name_out = "Italy",
                real_data = Daily_Absences_All_Staff$Staff_Absences_Covid_Perc,
                start_date_model = first_date, 
                end_date_model = params$end_date)

spain <- scenario_scaler(scenario_name = "Spain",
                name_out = "Spain",
                real_data = Daily_Absences_All_Staff$Staff_Absences_Covid_Perc,
                start_date_model = first_date, 
                end_date_model = params$end_date)

uk <- scenario_scaler(scenario_name = "UK",
                name_out = "UK",
                real_data = Daily_Absences_All_Staff$Staff_Absences_Covid_Perc,
                start_date_model = first_date, 
                end_date_model = params$end_date)

london <- scenario_scaler(scenario_name = "London",
                name_out = "London",
                real_data = Daily_Absences_All_Staff$Staff_Absences_Covid_Perc,
                start_date_model = first_date, 
                end_date_model = params$end_date)

cov_long <- rbind(devon, italy,spain, uk, london )
colnames(cov_long) <- c("date", "value", "name")


```


```{r, eval = FALSE}

ggplot(cov_long %>% 
         filter(date > params$plot_start_date),
       aes(
         x = date,
         y = value,
         group = name,
         col = name
       )) +
  geom_line(aes(
   # linetype = name,
    color = name,
    size = name
  )) +
  geom_point(data = cov_long %>% 
               filter(date <= first_date &
                      date > params$plot_start_date),
             col = "black") +
  ggtitle(paste0("Rt for ", params$hospital))+
  scale_size_manual(values = rep(2, length(unique(cov_long$name))))

  # scale_linetype_manual(values = c("twodash", "solid", "dotted", "solid")) +
  # scale_color_manual(values = c(rep("#F8766D", 3), "#00BFC4")) +
  # scale_size_manual(values = c(1, 1.5, 1, 1.5))


```
\newpage
#### Staff Absence Data\
Percentages of `r params$hospital` staff absences from `r min(Daily_Absences_All_Staff$Date)` to `r max(Daily_Absences_All_Staff$Date)`


```{r}
knitr::kable(Daily_Absences_All_Staff %>%
        select(Date, Staff_Absences_Perc,Staff_Absences_Covid_Perc,Staff_Absences_NoCovid_Perc) %>% 
        mutate(Staff_Absences_Perc = round(Staff_Absences_Perc *100,2),
               Staff_Absences_Covid_Perc = round(Staff_Absences_Covid_Perc * 100,2),
               Staff_Absences_NoCovid_Perc = round(Staff_Absences_NoCovid_Perc *100,2)), col.names = c("Date", "Total Staff Absences (%)", "Staff Absences due to COVID-19 (%)", "Other Staff Absences (%)"))


```


```{r}

Number_Staff_By_Group <- read_excel(paste0(params$in_dir,params$in_file), "Number_Staff_By_Group", col_names = TRUE) %>% 
  select(Group, FTE, Number_Staff) %>% 
  filter(!Group %in% c("Students", "Total"))

Number_Staff_By_Group$FTE <- as.numeric(Number_Staff_By_Group$FTE)

Number_Staff_By_Group$Number_Staff <- as.numeric(Number_Staff_By_Group$Number_Staff)

staff_num <- sum(Number_Staff_By_Group$Number_Staff)
group_max <- max(Number_Staff_By_Group$Number_Staff)

```


```{r Group Weights}
staff_weights <-
  read_excel(paste0(params$in_dir, params$in_file), "Absences_By_Group", col_names = TRUE) %>%
  filter(!Group %in% c("Total", "Students")) %>%
  drop_na() %>%
  left_join(., Number_Staff_By_Group, by = "Group") %>%
  mutate(
    Staff_Absences_Perc = as.numeric(Staff_Absences_Perc) / 100,
    Staff_Absences_Covid_Perc = as.numeric(Staff_Absences_Covid_Perc)/100,
    Staff_Absences_No_Covid_Perc = Staff_Absences_Perc - Staff_Absences_Covid_Perc,
    Num_Absent_Cov = Staff_Absences_Covid_Perc * Number_Staff,
    Num_Absent_No_Cov = Staff_Absences_No_Covid_Perc * Number_Staff,
    Weights_Covid_Absences_By_Group = Num_Absent_Cov / sum(Num_Absent_Cov),
    Weights_No_Covid_Absences_By_Group =
      Num_Absent_No_Cov / sum(Num_Absent_No_Cov)
  ) %>%
  select(
    Group,
    Number_Staff,
    Num_Absent_Cov,
    Num_Absent_No_Cov,
    Staff_Absences_Covid_Perc,
    Weights_Covid_Absences_By_Group,
    Weights_No_Covid_Absences_By_Group
  )
```


```{r, Future Non Covid Absences}
daily_abs_dates <-
  seq(min(cov_long$date), params$end_date, by = "day")

daily_abs <-
  c(
    Daily_Absences_All_Staff$Staff_Absences_NoCovid_Perc,
    rep(
      tail(Daily_Absences_All_Staff$Staff_Absences_NoCovid_Perc, 1),
      length(daily_abs_dates) - nrow(Daily_Absences_All_Staff)
    )
  )

no_cov_abs <-
  data.frame(date = daily_abs_dates, no_cov_abs = daily_abs)

```

```{r}

combs <-
  expand.grid(group = unique(staff_weights$Group),
              model = unique(cov_long$name))

group_df <- data.frame()
for (i in 1:nrow(combs)) {
  group = combs$group[i]
  model = combs$model[i]
  
  staff_group <- staff_weights %>%
    filter(Group == group)
  
  cov_rates <- cov_long %>%
    filter(name == model)
  
  cov_staff_out <-
    sum(staff_weights$Number_Staff) * staff_group$Weights_Covid_Absences_By_Group * cov_rates$value
  
  no_cov_staff_out <-
    sum(staff_weights$Number_Staff) * staff_group$Weights_No_Covid_Absences_By_Group * no_cov_abs$no_cov_abs
  
  total_staff_out <- cov_staff_out + no_cov_staff_out
  
  num_staff <-  staff_group$Number_Staff
  group_out <- data.frame(
    date = cov_rates$date,
    group = group,
    model = model,
    cov_staff_out = cov_staff_out,
    no_cov_staff_out = no_cov_staff_out,
    total_staff_out = total_staff_out,
    num_staff = num_staff,
    cov_prop_staff_out = (cov_staff_out / num_staff) *
      100,
    no_cov_prop_staff_out = (no_cov_staff_out / num_staff) *
      100,
    total_prop_staff_out = (total_staff_out / num_staff) *
      100
  )
  
  group_df <- rbind(group_out, group_df)
}


```

```{r, warnings =FALSE}

#2 week lag - people returning after 2 weeks

lag <- 14

# group_df_lag <- group_df %>%
#   group_by(group, model) %>%
#   mutate(
#     nrows = n(),
#     end_lag = nrows[1] - lag ,
#     cov_staff_return = ifelse(nrows > lag, c(rep(0, lag), cov_staff_out[1:end_lag]), 0))

group_df_lag <- group_df %>%
  group_by(group, model) %>%
  mutate( nrows = n(),
        end_lag = nrows[1] - lag ,
    diff_staff_cov = c(NA, diff(cov_staff_out)),
    cov_staff_return_day = ifelse(nrows >= lag, c(rep(0, lag), diff_staff_cov[1:end_lag]), 0))
```


```{r}
###############Only getting returners from 14days after last observed data point
group_df_lag$cov_staff_return_day <- ifelse(group_df_lag$date <= first_date + lag, 0 ,group_df_lag$cov_staff_return_day)

uniform_ret <- group_df_lag %>%
   group_by(group, model) %>%
   filter(date == first_date) %>% 
   mutate(uniform_return = cov_staff_out / lag) %>%
   ungroup() %>% 
   select(group, uniform_return) %>% 
   distinct()

dates <- seq(first_date + 1, first_date+14, by = "day")
groups <- rep(uniform_ret$group, each = length(dates))

df <- data.frame(date = dates, group = groups)
dfu <- merge(df, uniform_ret)

dft <- merge(group_df_lag, dfu, all = TRUE)

group_df_lag <- dft

group_df_lag$uniform_return[is.na(group_df_lag$uniform_return)]<-0

group_df_lag$cov_staff_return_day <- group_df_lag$cov_staff_return_day + group_df_lag$uniform_return

group_df_lag <- group_df_lag %>%
  group_by(group, model) %>%
  mutate(cov_staff_return = cumsum(cov_staff_return_day)) %>%
  ungroup() 
```

```{r}
# dates <- rep(seq(min(group_df_lag$date), max(group_df_lag$date), by = "day"),nrow(uniform)*length(scenarios))
# 
# df <- data.frame(group = groups, date = dates)
# dfu <- merge(df, uniform )
# 
# dfu$uniform_return[dfu$date <= first_date | dfu$date >= first_date+ 13] <- 0
# 
# group_df_lag<- unique(merge(dfu, group_df_lag, by = c("group", "date")))
# 
# 
# group_df_lag$cov_staff_return <- group_df_lag$cov_staff_return + group_df_lag$uniform_return

###############

#group_df_lag$cov_staff_out <- group_df_lag$cov_staff_out - group_df_lag$cov_staff_return

group_df_lag$cov_lag_prop <- (group_df_lag$cov_staff_out / group_df_lag$num_staff) * 100

group_df_lag$total_staff_out <- group_df_lag$cov_staff_out + group_df_lag$no_cov_staff_out

group_df_lag$total_prop_staff_out <- (group_df_lag$total_staff_out / group_df_lag$num_staff) * 100

group_df_lag <- group_df_lag %>% 
  select(
    date,
    group,
    model,
    cov_staff_out,
    cov_staff_out,
    cov_staff_return,
    no_cov_staff_out,
    total_staff_out,
    cov_prop_staff_out,
    cov_lag_prop,
    no_cov_prop_staff_out,
    total_prop_staff_out
  )


```


```{r, eval = FALSE}

write.csv(group_df_lag, paste0(params$out_dir,"/",params$hospital,"_",format(Sys.Date(), "%Y%m%d"), "_absences_data.csv"), row.names = FALSE)

```


```{r Date for group plots}
num_pl_df <- data.frame(group_df_lag %>% 
  select(date, group, model,total_staff_out, cov_staff_out) %>% 
  pivot_longer(., cols = c("total_staff_out", "cov_staff_out"))) %>% mutate(model = factor(model, levels = scenarios))

```



```{r Data for all staff plots}
all_staff<- data.frame(num_pl_df %>% 
              group_by(date, model, name) %>% 
              summarise(value = sum(value)) %>%               
              select(date, model,  name, value) %>% 
              ungroup())
```



```{r Total staff absent due to COVID}

ymax <- ifelse(max(all_staff$value)> staff_num, staff_num, NA)


all_staff_plot_cov <- ggplot(all_staff %>% filter(date > params$plot_start_date & name == "cov_staff_out"),aes(x = date, y = value, col = model, group = interaction(model,name)))+
 # geom_line(aes(linetype = model)), size = model)) +
  geom_line(size = 1)+
  geom_point(data = all_staff %>% filter(date > params$plot_start_date & date <= first_date & name == "cov_staff_out") , col = "black") +
  geom_vline(xintercept = first_date, linetype = "dotted") +
  ylab("Number Staff Absent")+
  xlab("Date")+
 # scale_color_manual(values = c("#00BFC4",rep("#F8766D", 3))) +
#  scale_linetype_manual(values = c("solid", "solid", "dotted", "dotted"))+
  scale_size_manual(values = rep(2, length(unique(all_staff$model))))+
  theme(legend.title = element_blank()) +
  ggtitle(paste0("Staff Numbers Absent due to COVID-19 - ", params$hospital))+
  labs(color = "", size = "", linetype= "")+
  theme_bw() +
  theme(text = element_text(size=20))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  scale_y_continuous(limits = c(NA,ymax))+
  guides(colour = guide_legend(override.aes = list(size = 2)))

```



\newpage
```{r, echo = FALSE}


png(paste0(params$out_dir,"/",params$hospital, "_",format(Sys.Date(), "%Y%m%d"),"_COVID_Absences_Numbers_All_Staff.png"), width = params$fig_width, height = params$fig_height, units = "in",res = params$image_ppi)
print(all_staff_plot_cov)
invisible(dev.off())

# ggsave(paste0(params$out_dir,"/",params$hospital, "_",format(Sys.Date(), "%Y%m%d"),"_COVID_Absences_Numbers_All_Staff.png"), width = 30, height = 20, units = "cm")

```


```{r Total staff absences}

all_staff_plot_total <- ggplot(all_staff %>% filter(date > params$plot_start_date & name == "total_staff_out"),aes(x = date, y = value, col = model, group = interaction(model,name)))+
  geom_line(size = 1)+
  # geom_line(aes(linetype = model, size = model)) +
  geom_point(data = all_staff %>% filter(date > params$plot_start_date & date <= first_date & name == "total_staff_out") , col = "black") +
  geom_vline(xintercept = first_date, linetype = "dotted") +
  ylab("Number Staff Absent")+
  xlab("Date")+
 # scale_color_manual(values = c("#00BFC4",rep("#F8766D", 3))) +
#  scale_linetype_manual(values = c("solid", "solid", "dotted", "dotted"))+
  scale_size_manual(values = rep(2, length(unique(all_staff$model))))+
  theme(legend.title = element_blank()) +
  ggtitle(paste0("Staff Numbers Absent (All) - ", params$hospital))+
  labs(color = "", size = "", linetype= "")+
  theme_bw() +
  theme(text = element_text(size=20))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  scale_y_continuous(limits = c(NA,ymax))+
  guides(colour = guide_legend(override.aes = list(size = 2)))


all_staff_plot_cov/all_staff_plot_total



```

```{r, echo =FALSE}


png(paste0(params$out_dir,"/",params$hospital, "_",format(Sys.Date(), "%Y%m%d"),"_All_Absences_Numbers_All_Staff.png"), width = params$fig_width, height = params$fig_height, units = "in",res = params$image_ppi)
print(all_staff_plot_total)
invisible(dev.off())

# ggsave(paste0(params$out_dir,"/",params$hospital, "_",format(Sys.Date(), "%Y%m%d"),"_All_Absences_Numbers_All_Staff.png"), width = 30, height = 20, units = "cm")
```


```{r Proportion plot data preparation}

prop_pl_df <- group_df_lag %>% 
  select(date, group, model,total_prop_staff_out, cov_lag_prop, no_cov_prop_staff_out) %>% 
  pivot_longer(., cols = c("total_prop_staff_out", "cov_lag_prop")) 

prop_pl_df$model <- factor(prop_pl_df$model, levels = scenarios)
```



```{r Total staff percentage absent due to COVID}
total_staff <- sum(Number_Staff_By_Group$Number_Staff[1:8])

all_staff$prop_value <- (all_staff$value /total_staff) *100


all_props_cov <- ggplot(all_staff %>% filter(date > params$plot_start_date & name == "cov_staff_out"),aes(x = date, y = prop_value, col = model, group = interaction(model, name)))+
  geom_line(size = 1)+
  #geom_line(aes(linetype = model, size = model)) +
  geom_point(data = all_staff %>% filter(date > params$plot_start_date & date <= first_date & name == "cov_staff_out") , col = "black") +
  geom_vline(xintercept = first_date, linetype = "dotted") +
   ylab("Proportion Staff Absent %")+
  xlab("Date")+
  #scale_color_manual(values = c("#00BFC4",rep("#F8766D", 3))) +
  #scale_linetype_manual(values = c("solid", "solid", "dotted", "dotted"))+
  scale_size_manual(values = rep(2, length(unique(all_staff$model))))+
  theme(legend.title = element_blank()) +
  theme_bw()+
  theme(text = element_text(size=20))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  ggtitle(paste0("Percentage Staff Absent due to COVID-19 - ", params$hospital))+
  labs(color = "", size = "", linetype= "")+
   scale_y_continuous(limits = c(NA,ymax))+
  guides(colour = guide_legend(override.aes = list(size = 2)))

#all_props_cov




```


```{r, echo = FALSE}


png(paste0(params$out_dir,"/",params$hospital, "_",format(Sys.Date(), "%Y%m%d"),"_COVID_Absences_Proportions_All_Staff.png"), width = params$fig_width, height = params$fig_height, units = "in",res = params$image_ppi)
print(all_props_cov)
invisible(dev.off())

# ggsave(paste0(params$out_dir,"/",params$hospital, "_",format(Sys.Date(), "%Y%m%d"),"_COVID_Absences_Proportions_All_Staff.png"), width = 30, height = 20, units = "cm")
```

```{r Total staff percentage absent}
total_staff <- sum(Number_Staff_By_Group$Number_Staff[1:8])

all_staff$prop_value <- (all_staff$value /total_staff) *100


all_props_tot <- ggplot(all_staff %>% filter(date > params$plot_start_date & name == "total_staff_out"),aes(x = date, y = prop_value, col = model, group = interaction(model, name)))+
  geom_line(size = 1)+
  # geom_line(aes(linetype = model, size = model)) +
  geom_point(data = all_staff %>% filter(date > params$plot_start_date & date <= first_date & name == "total_staff_out") , col = "black") +
  geom_vline(xintercept = first_date, linetype = "dotted") +
   ylab("Proportion Staff Absent %")+
  xlab("Date")+
  #scale_color_manual(values = c("#00BFC4",rep("#F8766D", 3))) +
  #scale_linetype_manual(values = c("solid", "solid", "dotted", "dotted"))+
  scale_size_manual(values = rep(2, length(unique(all_staff$model))))+
  theme(legend.title = element_blank()) +
  theme_bw()+
  theme(text = element_text(size=20))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  ggtitle(paste0("Percentage Staff Absent (All) - ", params$hospital))+
  labs(color = "", size = "", linetype= "")+
  scale_y_continuous(limits = c(NA,ymax))+
  guides(colour = guide_legend(override.aes = list(size = 2)))

#all_props_tot



all_props_cov/all_props_tot

```


```{r, echo = FALSE}


png(paste0(params$out_dir,"/",params$hospital, "_",format(Sys.Date(), "%Y%m%d"),"_All_Absences_Proportions_All_Staff.png"), width = params$fig_width, height = params$fig_height, units = "in",res = params$image_ppi)
print(all_props_tot)
invisible(dev.off())

# ggsave(paste0(params$out_dir,"/",params$hospital, "_",format(Sys.Date(), "%Y%m%d"),"_All_Absences_Proportions_All_Staff.png"), width = 30, height = 20, units = "cm")
```

```{r Group plot - covid numbers}

ymax <- ifelse(max(num_pl_df$value)> staff_num, staff_num, NA)

num_plot_cov <-
  ggplot(num_pl_df %>% 
           filter(date > params$plot_start_date & name == "cov_staff_out"),
    aes(
      x = date,
      y = value,
      group = interaction(model, group)
    )
  ) +
  geom_line(aes(col = model))+
  # geom_line(aes(col = model, linetype = model, size = model)) +
  geom_point(data = num_pl_df %>% filter(date > params$plot_start_date & date <= first_date & name == "cov_staff_out") , col = "black") +
  geom_vline(xintercept = first_date, linetype = "dotted") +
  facet_wrap( ~ group) +
  ylab("Number Staff Absent") +
  xlab("Date") +
  theme(legend.title = element_blank()) +
  ggtitle(paste0("Staff Numbers Absent due to COVID-19 - ", params$hospital))+
  labs(color = "", size = "", linetype= "")+
  theme_bw()+
#  scale_color_manual(values = c("#00BFC4",rep("#F8766D", 3))) +
 # scale_linetype_manual(values = c("solid", "solid", "dotted", "dotted"))+
  theme(text = element_text(size=20))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  scale_size_manual(values = rep(2, length(unique(all_staff$model))))+
  scale_y_continuous(limits = c(NA,ymax))+
  guides(colour = guide_legend(override.aes = list(size = 2)))
 
num_plot_cov


```



```{r, echo = FALSE}


png(paste0(params$out_dir,"/",params$hospital, "_",format(Sys.Date(), "%Y%m%d"),"_COVID_Absences_Numbers_Staff_Groups.png"), width = params$fig_width, height = params$fig_height, units = "in",res = params$image_ppi)
print(num_plot_cov)
invisible(dev.off())

# ggsave(paste0(params$out_dir,"/",params$hospital, "_",format(Sys.Date(), "%Y%m%d"),"_COVID_Absences_Numbers_Staff_Groups.png"), width = 30, height = 20, units = "cm")
```

```{r Group plot all absences}

num_plot_all <-
  ggplot(num_pl_df %>% 
           filter(date > params$plot_start_date & name == "total_staff_out"),
    aes(
      x = date,
      y = value,
      group = interaction(model, group)
    )
  ) +
  geom_line(aes(col = model))+
  # geom_line(aes(col = model, linetype = model, size = model)) +
  geom_point(data = num_pl_df %>% filter(date > params$plot_start_date & date <= first_date & name == "total_staff_out") , col = "black") +
  geom_vline(xintercept = first_date, linetype = "dotted") +
  facet_wrap( ~ group) +
  ylab("Number Staff Absent") +
  xlab("Date") +
#  scale_color_manual(values = c("#00BFC4",rep("#F8766D", 3))) +
#  scale_linetype_manual(values = c("solid", "solid", "dotted", "dotted"))+
  theme(legend.title = element_blank())+
  ggtitle(paste0("Staff Numbers Absent (All) - ", params$hospital))+
  labs(color = "", size = "", linetype= "")+
  theme_bw() +
  theme(text = element_text(size=20))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  scale_size_manual(values = rep(2, length(unique(num_pl_df$model))))+
  scale_y_continuous(limits = c(NA,ymax))
 
num_plot_all



```

```{r, echo = FALSE}


png(paste0(params$out_dir,"/", params$hospital, "_",format(Sys.Date(), "%Y%m%d"),"_All_Absences_Numbers_Staff_Groups.png"), width = params$fig_width, height = params$fig_height, units = "in",res = params$image_ppi)
print(num_plot_all)
invisible(dev.off())

# ggsave(paste0(params$out_dir,"/", params$hospital, "_",format(Sys.Date(), "%Y%m%d"),"_All_Absences_Numbers_Staff_Groups.png"), width = 30, height = 20, units = "cm")
```


```{r Group plot percentage staff absent due to COVID}
prop_plot_cov <- ggplot(prop_pl_df %>% filter(date > params$plot_start_date & name == "cov_lag_prop"),aes(x = date, y = value, col = model, group = interaction(model, group,name)))+
  geom_line(aes(col = model))+
  # geom_line(aes(col = model, linetype = model, size = model)) +
  geom_point(data = prop_pl_df %>% filter(date > params$plot_start_date & date <= first_date & name == "cov_lag_prop") , col = "black") +
  geom_vline(xintercept = first_date, linetype = "dotted") +
  facet_wrap(~group)+
  ylab("Proportion Staff Absent %")+
  xlab("Date")+
 # scale_color_manual(values = c("#00BFC4",rep("#F8766D", 3))) +
 #  scale_linetype_manual(values = c("solid", "solid", "dotted", "dotted"))+
  theme(legend.title = element_blank()) +
  theme_bw()+
  theme(text = element_text(size=20))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  ggtitle(paste0("Percentage Staff Absent due to COVID-19 - ", params$hospital))+
  labs(color = "", size = "", linetype= "")+
   scale_size_manual(values = rep(2, length(unique(prop_pl_df$model))))+
  scale_y_continuous(limits = c(NA,ymax))+
  guides(colour = guide_legend(override.aes = list(size = 2)))

prop_plot_cov



```


```{r, echo = FALSE}


png(paste0(params$out_dir,"/",params$hospital, "_",format(Sys.Date(), "%Y%m%d"),"_COVID_Absences_Proportions_Staff_Groups.png"), width = params$fig_width, height = params$fig_height, units = "in",res = params$image_ppi)
print(prop_plot_cov)
invisible(dev.off())

# ggsave(paste0(params$out_dir,"/",params$hospital, "_",format(Sys.Date(), "%Y%m%d"),"_COVID_Absences_Proportions_Staff_Groups.png"), width = 30, height = 20, units = "cm")
```


```{r Group plot all staff absences}

prop_plot_all <- ggplot(prop_pl_df %>% filter(date > params$plot_start_date & name == "total_prop_staff_out"),aes(x = date, y = value, col = model, group = interaction(model, group,name)))+
  geom_line(aes(col = model))+
  #geom_line(aes(col = model, linetype = model, size = model)) +
  geom_point(data = prop_pl_df %>% filter(date > params$plot_start_date & date <= first_date & name == "total_prop_staff_out") , col = "black") +
  geom_vline(xintercept = first_date, linetype = "dotted") +
  facet_wrap(~group)+
  ylab("Proportion Staff Absent %")+
  xlab("Date")+
 # scale_color_manual(values = c("#00BFC4",rep("#F8766D", 3))) +
 #  scale_linetype_manual(values = c("solid", "solid", "dotted", "dotted"))+
  theme(legend.title = element_blank()) +
  theme_bw()+
  theme(text = element_text(size=20))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  ggtitle(paste0("Percentage Staff Absent (All)- ", params$hospital))+
  labs(color = "", size = "", linetype= "")+
  scale_size_manual(values = rep(2, length(unique(prop_pl_df$model))))+
  scale_y_continuous(limits = c(NA,ymax))+
  guides(colour = guide_legend(override.aes = list(size = 2)))


prop_plot_all


```


```{r, echo = FALSE}


png(paste0(params$out_dir,"/",params$hospital, "_",format(Sys.Date(), "%Y%m%d"),"_All_Absences_Proportions_Staff_Groups.png"), width = params$fig_width, height = params$fig_height, units = "in",res = params$image_ppi)
print(prop_plot_all)
invisible(dev.off())

# 
# ggsave(paste0(params$out_dir,"/",params$hospital, "_",format(Sys.Date(), "%Y%m%d"),"_All_Absences_Proportions_Staff_Groups.png"), width = 30, height = 20, units = "cm")

```

